%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Logistics and Distribution IT Develop \& Software Engineer} % Job title
    {CJ Olivenetworks} % Organization
    {Seoul, S.Korea} % Location
    {Jan. 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Warehouse Management System and Automated Logistics Control System}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Software Maestro (funded by Korea Ministry of Knowledge and Economy)} % Organization
    {Seoul, S.Korea} % Location
    {Aug. 2017 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of sports player motion analysis system based on Tensorflow.}
        \item {Develop improved the K-Means algorithm for sports analysis.}
        \item {Design and Implementation of Intelligent Remote Tactical Monitoring System based on camera and image distortion correction technology for sports player and coach(Published related papers in the 2018 Korea Computer Science Conference.}
        \item {Received the Science and Technology Information and Communication Minister's Award at the Software Talent Festival in 2018.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Manager of BackEnd Developer(Sergeant) \& Software Engineer} % Job title
    {R.O.K Cyber Command, MND } % Organization
    {Seoul, S.Korea} % Location
    {Aug. 2014 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implementation of server authentication / authorization function of RBAC Model and applied to request filter.}
        \item {Web service development based on Tomcat7 (Java), Apache2, and PostgreSQL 9.3 Stack.}
        \item {Apply Java Hibernate-based DAO pattern (using Criteria, HQL).}
        \item {Implement REST API Web Service using Java Jersey.}
        \item {Development of Python Tornado-based Web API Server Function.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Founder \& Software Engineer} % Job title
    {Qode Interactive Corp. (Start-up company)} % Organization
    {Seoul, S.Korea} % Location
    {Apr. 2013 - Feb. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Eat + Entertainment develops next-generation sensible smart board game machine.}
        \item {Built a server that links Android and Hardware (Smart Game Table) using Arduino, Node.js. (IoT System)}
        \item {Developed a system to control and play game the hardware(smart game table). by connecting the smartphone to the web, the connected smartphone became a joystick.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Founder \& Software Engineer} % Job title
    {Moduparking (Start-up company)} % Organization
    {Seoul, S.Korea} % Location
    {Sep. 2012 - Mar. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Android Service.}
        \item {Korea's first parking reservation mobile application.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
